Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-08-10 paper.tex
Updated abstract

\begin{abstract}
  Splitting and merging data is a requirement for most parallel or
  distributed processing operations. Naive algorithms, however,
  perform very poorly to split or merge 3D blocks from ultra-high
  resolution images, due to important seek times. We propose and
  analyze two algorithms based on in-memory reconstruction of image
  parts. Cluster reads access image chunks only once while Multiple
  reads minimize the accesses to the image. Evaluation on a
  3850x3025x3500 brain image shows that our algorithms perform
  similarly to the optimal configuration (slice merging) provided that
  enough memory is available, which solves our initial problem.  We
  conclude that splitting and merging large 3D images can be done
  efficiently based on simple data formats.
\end{abstract}

>>>>

\begin{abstract}
  Splitting and merging data is a requirement for most parallel or
  distributed processing operations. Naive algorithms, however,
  perform very poorly to split or merge 3D blocks from ultra-high
  resolution images, due to important seek times. We introduce and
  analyze sequential algorithms that leverage memory buffering, to
  address this issue. Cluster reads and Cluster writes access image
  chunks only once, but they have to seek in the reconstructed
  image. Multiple reads and Multiple writes minimize seeks in the
  reconstructed image, but they access image chunks multiple
  times. Evaluation on a 3850x3025x3500 brain image shows that our
  algorithms perform similarly to the optimal configuration (slice
  merging) provided that enough memory is available, which solves our
  initial problem to a large extent.  We conclude that splitting and
  merging large 3D images can be done efficiently without the need for
  complex data formats.
\end{abstract}
